Covariate analysis of UFL-Mayo-ISB RNASeq temporal cortex

### 2016-02-02 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum"
author: "Thanneer Perumal"
date: '`r date()`'
output:
  html_document: default
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)

@@

# Initial design matrix with covariates under consideration
DM = getDesignMatrix(COVARIATES, Intercept = F)
```
Clustering of initial normalised data (with NULL design)
```{r decompse_normalise_data, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E)

@@

### Clustering residual gene expression
```{r decompse_normalise_data1, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1)], scale.=T)

>>>>

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum"
author: "Thanneer Perumal"
date: '`r date()`'
output: "html_document"
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)

@@

# Initial design matrix with covariates under consideration
DM = getDesignMatrix(COVARIATES, Intercept = F)
```
Clustering of initial normalised data (with NULL design)
```{r decompse.normalise.data1, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E)

@@

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1)], scale.=T)

### 2016-02-02 code/Rmd/Mayo_TemporalCortex_RNASeq.Rmd

knit2synapse::knitToFolderEntity(file = "./Mayo_TemporalCortex_RNASeq.Rmd",
                                 parentId ='syn5612983',#"syn5570325",
                                 entityName = 'UFL_Mayo_ISB Temporal Cortex RNASeq')
```

@@

```{r synapse.parameters, include=FALSE}
# Synapse parameters
parentId = 'syn5612983'#'syn5570325';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of UFL_Mayo_ISB temporal cortex RNASeq data';

>>>>

knit2synapse::knitToFolderEntity(file = "./Mayo_TemporalCortex_RNASeq.Rmd",
                                 parentId = "syn5570325",
                                 entityName = 'UFL_Mayo_ISB Temporal Cortex RNASeq')
```

@@

```{r synapse.parameters, include=FALSE}
# Synapse parameters
parentId = 'syn5570325';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of UFL_Mayo_ISB temporal cortex RNASeq data';
